Hyperplane Elimination for Quickly Enumerating Local Optima

### 2015-09-09 Hyperplane Enumeration/main.tex
Added figures to text, added table, changed some results section titles

\section{Timing Comparisons}
\subsection{Increasing problem size}
Consider including boxplots of largest size all are successful.

\subsection{The Effect of Radius}

>>>>

\section{Finding Local Optima}
TODO Concatenated Traps using $N>40$ has slope of 2.
\begin{figure*}
  \centering
  \includegraphicsfit{length-method}
  \caption{Comparison of how each method scales with problem size on log-linear scales. Each point is the mean
           runtime over 30 instances and each line the linear model. All confidence intervals too tight to see.}
  \label{fig-length-method}
\end{figure*}

\begin{table}
	\centering
	\caption{Value of $m$ when fitting a model to $y = 2^c2^{mN}$ where $y$ is number of seconds required to
	         find all local optima of a problem using $N$ bits. Optimal refers to the same model where
	         $y$ is the number of local optima.}
	\begin{tabular}{|r|c|c|c|c|}
	  \hline
	    & \textbf{Gray-Box} & \textbf{Hyper} & \textbf{Hyper-Reorder} & \textbf{Optimal} \\ \hline
	  Concatenated Traps & 0.9809 & 0.5765 & 0.1601 & 0.2000 \\ \hline
    Adjacent NKq & 0.9922 & 0.5972 & 0.3411 & 0.3603 \\ \hline
    Random NKq & 0.9920 & 0.6202 & 0.3984 & 0.3531 \\ \hline
    Ising Spin Glass & 0.9821 & 0.6576 & 0.5909 & 0.6015 \\ \hline
    MAX-kSAT & 0.9949 & 0.8893 & 0.7735 & 0.5393 \\ \hline
  \end{tabular}
  \label{table-results}
\end{table}

\begin{figure*}
  \centering
  \includegraphicsfit{boxplot-method}
  \caption{Comparison of completion time variance for the largest size of each problem
           where all three methods were fully successful.}
  \label{fig-boxplot-method}
\end{figure*}

\section{Finding $r$-Bit Local Optima}
